|

### 2025-02-09 paper.Rmd
Change one sentence in the abstract.
Change font size for letters in Figures

During the last week of the study period, among females aged 30, opportunistic screening was associated with a greater HPV infection prevalence for HPV16 and/or 18 (other genotypes) in `r results$map[[30]]$count_difference_test %>% filter(virusgroup == 1) %>% function_text(., x = 1, y = 1, multiple = 100, ref = nrow(data_cp_final))`% (`r results$map[[30]]$count_difference_test %>% filter(virusgroup == 2) %>% function_text(., x = 1, y = 1, multiple = 100, ref = nrow(data_cp_final))`%) of postcodes. The probability for this percentage to be lower among females aged 66 was below 95% for both genotype groups.

@@

```{r include=FALSE}
p1 <- ggpubr::ggarrange(
 descriptivefigures$descriptive_plot_sample + 
  scale_y_continuous(labels = function(x) ifelse(x < 0, "", scales::comma(x)), n.breaks = 10) +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom"),
 descriptivefigures$number_test_age +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  theme(axis.text.x = element_text(angle = +90, vjust = 0.5, hjust=1)),
 ncol = 2,
 labels = c("A) ", "B) "),
 font.label = list(size = 22, color = "black", face = "bold", family = NULL)
)
p2 <- ggpubr::ggarrange(
 descriptivefigures$descriptive_plot_year +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom"),
 descriptivefigures$descriptive_plot_age +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  theme(axis.text.x = element_text(angle = +90, vjust = 0.5, hjust=1)),
 ncol = 2,
 labels = c("C) ", "D) "),
 font.label = list(size = 22, color = "black", face = "bold", family = NULL)
)

@@

plot_year <- results$list_main_city$summary_city_year %>% 
  filter(metric == "rd") %>% 
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test), size = 1)+
  geom_ribbon(aes(x = age,
           ymin = qi_lb, 
           ymax = qi_ub,
           fill = test), alpha = 0.25) +
  facet_grid(genotypes~city) +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Year",
     y = "Difference in expected prevalence \n between 2023 and 2020",
     color = "Type of screening: ",
     fill = "Type of screening: ",
     caption = "Line: posterior average. Ribbon: posterior ETI95%. Scale of y axis for plots B and C: percentage points.") +
  scale_fill_manual(values = c("red", "blue")) +
  scale_color_manual(values = c("red", "blue")) +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = function(x)100*x)

plot_age <- results$list_main_city$summary_city_age %>% 
  filter(metric == "rd") %>% 
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test), size = 1)+
  geom_ribbon(aes(x = age,
           ymin = qi_lb, 
           ymax = qi_ub,
           fill = test), alpha = 0.25) +
  facet_grid(genotypes~city, scale = 'free_y') +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Age",
     y = "Difference in expected prevalence \n with females aged 30",
     color = "Type of screening: ",
     fill = "Type of screening: ",
     caption = "Line: posterior average. Ribbon: posterior ETI95%. Scale of y axis for plots A and B: percentage points.") +
  scale_fill_manual(values = c("red", "blue")) +
  scale_color_manual(values = c("red", "blue")) +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = function(x)100*x)

@@

plot_summary_city <- results$list_main_city$virusspecific %>%
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test),linewidth = 1)+
  geom_ribbon(aes(x = age,
          ymin = qi_lb,
          ymax = qi_ub,
          fill = test), alpha = 0.25) +
  facet_grid(genotypes~city, scale = "free") +
  labs(x = "Age",
     y = "Expected prevalence in %",
     caption = "Line: posterior average. Ribbon: posterior ETI95%",
     color = "Type of screening: ",
     fill = "Type of screening: ") +
  scale_fill_manual(values = c("red", "blue")) +
  scale_color_manual(values = c("red", "blue")) +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom") +
  scale_y_continuous(labels = scales::percent)

library(ggnewscale)
diff_between_virus_city <- results$list_main_city$difference_virus %>%
  filter(idtime == max(idtime)) %>% 
 plyr::rbind.fill(results$list_main_city$difference_virus_test %>%
     filter(idtime == max(idtime)) %>% 
     mutate(test = NA)) %>% 
 mutate(test = case_when(
  test == "Organised" ~ "Difference in expected prevalence between other genotypes and HPV16/18, correcting for the systematic inflation associated with opportunistic screening (percentage points)",
    test == "Opportunistic" ~ "Difference in expected prevalence between other genotypes and HPV16/18, under opportunistic screening (percentage points)",
  T ~ "Systematic inflation associated with opportunistic screening in the difference between expected prevalence of each genotype group (percentage points)"
  )
 ) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test),linewidth = 1)+
  geom_ribbon(aes(x = age,
          ymin = qi_lb,
          ymax = qi_ub,
          fill = test), alpha = 0.25) +
  facet_grid(~city) +
  labs(x = "Age",
     y = "Posterior average (solid line) and ETI95% (ribbon)",
     color = "Difference between HPV16/18 and other genotypes: ",
     fill = "Difference between HPV16/18 and other genotypes: ",
     caption = element_blank()) +
  scale_fill_manual(values = c("red", "blue", "darkgreen")) +
  scale_color_manual(values = c("red", "blue", "darkgreen")) +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  #geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(labels = function(x)100*x) +
 guides(fill=guide_legend(nrow=3,byrow=TRUE),
     color=guide_legend(nrow=3,byrow=TRUE))+ 
 labs(color = element_blank(),
    fill = element_blank())

diff_between_test_city <- results$list_main_city$difference_test %>%
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = genotypes),linewidth = 1)+
  geom_ribbon(aes(x = age,
          ymin = qi_lb,
          ymax = qi_ub,
          fill = genotypes), alpha = 0.25) +
  facet_grid(~city) +
  labs(x = "Age",
     y = "Difference in expected prevalence \n between opportunistic and organised screening",
     color = "Genotype group: ",
     fill = "Genotype group: ",
     caption = element_blank()) +
  scale_fill_manual(values = c("darkgreen", "darkorange")) +
  scale_color_manual(values = c("darkgreen", "darkorange")) +
  theme_minimal(base_size = 21) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(labels = function(x)paste0(100*x, "pp"))

ecdf_space <- results$map[[30]]$difference_test %>% st_drop_geometry()%>%
 mutate(virusgroup = ifelse(virusgroup == 1, "HPV16/18", "Other genotypes")) %>% 
 ggplot() + 
 stat_ecdf(aes(x = higher_0, color = virusgroup),geom = "smooth") + scale_color_manual(values = c("darkgreen", "darkorange"))+
 labs(x = "Posterior probability of systematic inflation > 0", y = "Cumulated proportion",color = "Virus") + 
 geom_vline(xintercept = 0.95, linetype = "dashed")+
 geom_hline(yintercept = 0.5, linetype = "dashed")+
 theme_minimal(base_size = 21) +
 theme(legend.direction = "horizontal", legend.position = "bottom")

@@

plot_number_cp <- change_number_cp %>% 
  pivot_longer(cols = c(mean, qi_lb, qi_ub),
               names_to = "name",
               values_to = "value") %>% 
  mutate(name = case_when(
           name == "mean" ~ "Average",
           name == "qi_lb" ~ "ETI95% LB",
           name == "qi_ub" ~ "ETI95% UB"
         ),
         name = factor(name, levels = c("ETI95% LB", "Average", "ETI95% UB"))) %>% 
  mutate(value = value/nrow(data_cp_final)) %>% 
    mutate(virusgroup = ifelse(virusgroup==1, "HPV16/18", "Other genotypes")) %>% 
    ggplot() +
    geom_line(aes(x = age, y = value,color = virusgroup, linetype = name)) +
    labs(color = "Genotype group: ",
         linetype = "Posterior: ")+ 
    theme_minimal(base_size = 21)  +
    scale_color_manual(values = c("darkgreen", "orange"))  + 
    scale_y_continuous(labels = scales::label_percent(), n.breaks = 8) +
  scale_linetype_manual(values = c(2,1, 3), labels = c("2.5% Quantile", "Average", "97.5% Quantile")) + 
  labs(x = "Age",
       y = str_wrap("Posterior % of postcodes with a greater expected infection \n prevalence under opportunistic screening, compared \n with organised screening", 40)) + 
  scale_x_continuous(breaks = seq(30, 66, 5))

diff_number_cp <- results$change_inflation_age %>% 
    imap(~.x$diff_prev_between_screening) %>% 
    do.call(rbind,.) %>% 
    select(age,
           mean,
           qi_lb,
           qi_ub,
           lower_0,
           virusgroup) %>% 
    mutate_at(c("mean",
                "qi_lb",
                "qi_ub"),
              ~round(.,0))  %>% 
  mutate(virusgroup = ifelse(virusgroup == 1, "HPV16/18", "Other genotypes")) %>% 
    ggplot() + 
    geom_line(aes(x = age, y = lower_0, color = factor(virusgroup))) +
    labs(color = "Genotype group: ",
         linetype = element_blank())+ 
    theme_minimal(base_size = 21)  +
    scale_color_manual(values = c("darkgreen", "orange"))  + 
    scale_y_continuous(labels = scales::label_percent(), n.breaks = 8) +
    scale_linetype_manual(values = c(2,1, 3), labels = c("2.5% Quantile", "Average", "97.5% Quantile")) + 
    labs(x = "Age",
         y = str_wrap("Posterior probability for the number of postcodes with a detected inflation in expected prevalence under opportunistic screening to be lower than this at age 30",  width = 40)) + 
    scale_x_continuous(breaks = seq(30, 66, 5))

@@

plot_expected_prevalence <- results$prevalence$expected_prevalence %>% 
  plyr::rbind.fill(results$prevalence$expected_prevalence_year) %>% 
  mutate(year = ifelse(is.na(year), "All", year),
      year = factor(year, levels = c("2020","2021","2022","2023","All")),
      virus = ifelse(virus == "hpv1618", "HPV16/18", "Other genotypes"),
      test = paste0(test, " screening")) %>% 
  ggplot() + 
  geom_point(position = position_dodge(width = 0.9),
        aes(x = year, y = mean, color = test))+
  geom_errorbar(position = position_dodge(width = 0.9),
         aes(x = year, ymin = qi_lb, ymax = qi_ub, color = test))+
  #geom_hline(yintercept = 0, linetype = "dashed")+
  labs(x = "Year",
     y = "Expected prevalence in \n the analytic sample",
     caption = "Posterior average: dots, Posterior ETI95%: bars",
     color = "Assuming all tests collected through: ")+ 
  theme_minimal(base_size = 21) +
  facet_grid(~virus)+
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = scales::label_percent(), n.breaks = 8)+
  scale_color_manual(values = c("red", "blue"))

plot_ame <- results$ame$ame_test %>% 
  plyr::rbind.fill(results$ame$ame_test_year) %>% 
  mutate(year = ifelse(is.na(year), "All", year),
      year = factor(year, levels = c("2020","2021","2022","2023","All")),
      virus = ifelse(virus == "hpv1618", "HPV16/18", "Other genotypes")) %>% 
  ggplot() + 
  geom_point(aes(x = year, y = mean, color = year))+
  geom_errorbar(aes(x = year, ymin = qi_lb, ymax = qi_ub, color = year))+
  #geom_hline(yintercept = 0, linetype = "dashed")+
  labs(x = "Year",
     y = "Marginal difference in expected prevalence  of opportunistic screening",
     caption = "Posterior average: dots, Posterior ETI95%: bars",
     color = "Year: ")+ 
  theme_minimal(base_size = 21) +
  facet_grid(~virus)+
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = function(x)100*x)

plot_ameage <- results$ame$ame_test_age %>% 
    plyr::rbind.fill(results$ame$ame_test %>% mutate(age_class = "[30,66]")) %>% 
    plyr::rbind.fill(results$ame$ame_test_year %>% mutate(age_class = "[30,66]")) %>% 
    plyr::rbind.fill(results$ame$ame_test_age_year) %>% 
    mutate(year = ifelse(is.na(year), "All", year),
           year = factor(year, levels = c("2020","2021","2022","2023","All")),
           virus = ifelse(virus == "hpv1618", "HPV16/18", "Other genotypes"),
           age_class = factor(age_class, levels = c("[30,39]", "(39,49]", "(49,59]", "(59,66]", "[30,66]"))) %>% 
    ggplot() + 
    geom_point(aes(x = year, y = mean, color = year))+
    geom_errorbar(aes(x = year, ymin = qi_lb, ymax = qi_ub, color = year))+
    facet_grid(age_class~virus) +
    #geom_hline(yintercept = 0, linetype = "dashed")+
    labs(x = "Year",
         y = "Marginal difference in expected prevalence  by age",
         caption = "Posterior average: dots, Posterior ETI95%: bars",
         color = "Year: ")+ 
    theme_minimal(base_size = 21) +
    theme(legend.direction = "horizontal", legend.position = "bottom")+
    scale_color_manual(values = c("darkorange", "purple", "darkgreen", "brown", "black"))+
    geom_hline(yintercept = 0, color = 'red', linetype = "dashed") + 
    scale_y_continuous(breaks = seq(0,0.06, 0.02), labels = function(x)paste0(100*x,"pp"))

plot_or_time <- results$list_main_city$summary_city_year %>% 
  filter(age == 30 &
        metric == "or" & 
        idtime != 1 & 
        city == "Paris") %>% 
  ggplot() +
  geom_point(aes(x = genotypes, y = mean, color = test ), position = position_dodge(width = 0.9))+
  geom_errorbar(aes(x = genotypes, ymin = qi_lb, ymax = qi_ub, color = test ), position = position_dodge(width = 0.9)) +
  theme_minimal()+
  geom_hline(yintercept = 1, linetype = "dashed") +
  scale_y_continuous(n.breaks = 8) +
  labs(x = "Genotypes",
     y = "Odds ratio of the expected \n prevalence  between the last \n and first week of the period",
     color = "Type of screening: ")+
  scale_color_manual(values = c("red", "blue")) +
   theme_minimal(base_size = 21) +
   theme(legend.direction = "horizontal", legend.position = "bottom") 
```

@@

p <- ggpubr::ggarrange(
ggpubr::ggarrange(
 space30_differencetest_hpv1618+
  labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none") +
  labs(subtitle = "Metropolitan France"),
 space30_differencetest_hpvother+ 
  labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none")+
  labs(subtitle = "Metropolitan France"),
 labels = c("A) ", "B) "),
 font.label = list(size = 22, color = "black", face = "bold", family = NULL)
 ),
ggpubr::ggarrange(
paris30_differencetest_hpv1618 +
  labs(subtitle = "Zoom on Paris region"),
paris30_differencetest_hpvother+
  labs(subtitle = "Zoom on Paris region"),
labels = c(" ", " "), 
nrow = 1),
heights = c(2,1),
nrow = 2)

@@

p <- ggpubr::ggarrange(
ggpubr::ggarrange(
france30_hpv1618 +
 labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none")+
  labs(subtitle = "Metropolitan France"),
france30_hpvother+
 labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none")+
  labs(subtitle = "Metropolitan France"),
labels = c("A) ", "B) "),
 font.label = list(size = 22, color = "black", face = "bold", family = NULL)),
ggpubr::ggarrange(
paris30_hpv1618+
  labs(subtitle = "Zoom on Paris region"),
paris30_hpvother+
  labs(subtitle = "Zoom on Paris region"),
labels = c(" ", "")),
heights = c(2,1),
nrow = 2)

@@

```{r}
plot_cp <- ggpubr::ggarrange(
    plot_number_cp,
    diff_number_cp,
  labels = c("C) ", "D) "),
 font.label = list(size = 22, color = "black", face = "bold", family = NULL),
 ncol = 2)
```

@@

ggpubr::ggarrange(
  plot_summary_city,
  diff_between_test_city,
  plot_cp,
  labels = c("A) ", "B) ", " "),
 font.label = list(size = 22, color = "black", face = "bold", family = NULL),
  nrow = 3)

@@

>>>>

During the last week of the study period, among females aged 30, opportunistic screening was associated with a greater HPV infection prevalence for HPV16 and/or 18 (other genotypes) in `r results$map[[30]]$count_difference_test %>% filter(virusgroup == 1) %>% function_text(., x = 1, y = 1, multiple = 100, ref = nrow(data_cp_final))`% (`r results$map[[30]]$count_difference_test %>% filter(virusgroup == 2) %>% function_text(., x = 1, y = 1, multiple = 100, ref = nrow(data_cp_final))`%) of postcodes. The probability of this percentage being lower among females aged 66 was below 95% for both genotype groups.

@@

```{r include=FALSE}
p1 <- ggpubr::ggarrange(
 descriptivefigures$descriptive_plot_sample + 
  scale_y_continuous(labels = function(x) ifelse(x < 0, "", scales::comma(x)), n.breaks = 10) +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom"),
 descriptivefigures$number_test_age +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  theme(axis.text.x = element_text(angle = +90, vjust = 0.5, hjust=1)),
 ncol = 2,
 labels = c("A) ", "B) "),
 font.label = list(size = 20, color = "black", face = "bold", family = NULL)
)
p2 <- ggpubr::ggarrange(
 descriptivefigures$descriptive_plot_year +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom"),
 descriptivefigures$descriptive_plot_age +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  theme(axis.text.x = element_text(angle = +90, vjust = 0.5, hjust=1)),
 ncol = 2,
 labels = c("C) ", "D) "),
 font.label = list(size = 20, color = "black", face = "bold", family = NULL)
)

@@

plot_year <- results$list_main_city$summary_city_year %>% 
  filter(metric == "rd") %>% 
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test), size = 1)+
  geom_ribbon(aes(x = age,
           ymin = qi_lb, 
           ymax = qi_ub,
           fill = test), alpha = 0.25) +
  facet_grid(genotypes~city) +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Year",
     y = "Difference in expected prevalence \n between 2023 and 2020",
     color = "Type of screening: ",
     fill = "Type of screening: ",
     caption = "Line: posterior average. Ribbon: posterior ETI95%. Scale of y axis for plots B and C: percentage points.") +
  scale_fill_manual(values = c("red", "blue")) +
  scale_color_manual(values = c("red", "blue")) +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = function(x)100*x)

plot_age <- results$list_main_city$summary_city_age %>% 
  filter(metric == "rd") %>% 
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test), size = 1)+
  geom_ribbon(aes(x = age,
           ymin = qi_lb, 
           ymax = qi_ub,
           fill = test), alpha = 0.25) +
  facet_grid(genotypes~city, scale = 'free_y') +
  #geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Age",
     y = "Difference in expected prevalence \n with females aged 30",
     color = "Type of screening: ",
     fill = "Type of screening: ",
     caption = "Line: posterior average. Ribbon: posterior ETI95%. Scale of y axis for plots A and B: percentage points.") +
  scale_fill_manual(values = c("red", "blue")) +
  scale_color_manual(values = c("red", "blue")) +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = function(x)100*x)

@@

plot_summary_city <- results$list_main_city$virusspecific %>%
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test),linewidth = 1)+
  geom_ribbon(aes(x = age,
          ymin = qi_lb,
          ymax = qi_ub,
          fill = test), alpha = 0.25) +
  facet_grid(genotypes~city, scale = "free") +
  labs(x = "Age",
     y = "Expected prevalence in %",
     caption = "Line: posterior average. Ribbon: posterior ETI95%",
     color = "Type of screening: ",
     fill = "Type of screening: ") +
  scale_fill_manual(values = c("red", "blue")) +
  scale_color_manual(values = c("red", "blue")) +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom") +
  scale_y_continuous(labels = scales::percent)

library(ggnewscale)
diff_between_virus_city <- results$list_main_city$difference_virus %>%
  filter(idtime == max(idtime)) %>% 
 plyr::rbind.fill(results$list_main_city$difference_virus_test %>%
     filter(idtime == max(idtime)) %>% 
     mutate(test = NA)) %>% 
 mutate(test = case_when(
  test == "Organised" ~ "Difference in expected prevalence between other genotypes and HPV16/18, correcting for the systematic inflation associated with opportunistic screening (percentage points)",
    test == "Opportunistic" ~ "Difference in expected prevalence between other genotypes and HPV16/18, under opportunistic screening (percentage points)",
  T ~ "Systematic inflation associated with opportunistic screening in the difference between expected prevalence of each genotype group (percentage points)"
  )
 ) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = test),linewidth = 1)+
  geom_ribbon(aes(x = age,
          ymin = qi_lb,
          ymax = qi_ub,
          fill = test), alpha = 0.25) +
  facet_grid(~city) +
  labs(x = "Age",
     y = "Posterior average (solid line) and ETI95% (ribbon)",
     color = "Difference between HPV16/18 and other genotypes: ",
     fill = "Difference between HPV16/18 and other genotypes: ",
     caption = element_blank()) +
  scale_fill_manual(values = c("red", "blue", "darkgreen")) +
  scale_color_manual(values = c("red", "blue", "darkgreen")) +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  #geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(labels = function(x)100*x) +
 guides(fill=guide_legend(nrow=3,byrow=TRUE),
     color=guide_legend(nrow=3,byrow=TRUE))+ 
 labs(color = element_blank(),
    fill = element_blank())

diff_between_test_city <- results$list_main_city$difference_test %>%
  filter(idtime == max(idtime)) %>% 
  ggplot() +
  geom_line(aes(x = age, y = mean, color = genotypes),linewidth = 1)+
  geom_ribbon(aes(x = age,
          ymin = qi_lb,
          ymax = qi_ub,
          fill = genotypes), alpha = 0.25) +
  facet_grid(~city) +
  labs(x = "Age",
     y = "Difference in expected prevalence \nbetween opportunistic and organised screening",
     color = "Genotype group: ",
     fill = "Genotype group: ",
     caption = element_blank()) +
  scale_fill_manual(values = c("darkgreen", "darkorange")) +
  scale_color_manual(values = c("darkgreen", "darkorange")) +
  theme_minimal(base_size = 20) +
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_y_continuous(labels = function(x)paste0(100*x, "pp"))

ecdf_space <- results$map[[30]]$difference_test %>% st_drop_geometry()%>%
 mutate(virusgroup = ifelse(virusgroup == 1, "HPV16/18", "Other genotypes")) %>% 
 ggplot() + 
 stat_ecdf(aes(x = higher_0, color = virusgroup),geom = "smooth") + scale_color_manual(values = c("darkgreen", "darkorange"))+
 labs(x = "Posterior probability of systematic inflation > 0", y = "Cumulated proportion",color = "Virus") + 
 geom_vline(xintercept = 0.95, linetype = "dashed")+
 geom_hline(yintercept = 0.5, linetype = "dashed")+
 theme_minimal(base_size = 20) +
 theme(legend.direction = "horizontal", legend.position = "bottom")

@@

plot_number_cp <- change_number_cp %>% 
  pivot_longer(cols = c(mean, qi_lb, qi_ub),
               names_to = "name",
               values_to = "value") %>% 
  mutate(name = case_when(
           name == "mean" ~ "Average",
           name == "qi_lb" ~ "ETI95% LB",
           name == "qi_ub" ~ "ETI95% UB"
         ),
         name = factor(name, levels = c("ETI95% LB", "Average", "ETI95% UB"))) %>% 
  mutate(value = value/nrow(data_cp_final)) %>% 
    mutate(virusgroup = ifelse(virusgroup==1, "HPV16/18", "Other genotypes")) %>% 
    ggplot() +
    geom_line(aes(x = age, y = value,color = virusgroup, linetype = name)) +
    labs(color = "Genotype group: ",
         linetype = "Posterior: ")+ 
    theme_minimal(base_size = 20)  +
    scale_color_manual(values = c("darkgreen", "orange"))  + 
    scale_y_continuous(labels = scales::label_percent(), n.breaks = 8) +
  scale_linetype_manual(values = c(2,1, 3), labels = c("2.5% Quantile", "Average", "97.5% Quantile")) + 
  labs(x = "Age",
       y = str_wrap("Posterior % of postcodes with a greater expected infection \n prevalence under opportunistic screening, compared \n with organised screening", 40)) + 
  scale_x_continuous(breaks = seq(30, 66, 5))

diff_number_cp <- results$change_inflation_age %>% 
    imap(~.x$diff_prev_between_screening) %>% 
    do.call(rbind,.) %>% 
    select(age,
           mean,
           qi_lb,
           qi_ub,
           lower_0,
           virusgroup) %>% 
    mutate_at(c("mean",
                "qi_lb",
                "qi_ub"),
              ~round(.,0))  %>% 
  mutate(virusgroup = ifelse(virusgroup == 1, "HPV16/18", "Other genotypes")) %>% 
    ggplot() + 
    geom_line(aes(x = age, y = lower_0, color = factor(virusgroup))) +
    labs(color = "Genotype group: ",
         linetype = element_blank())+ 
    theme_minimal(base_size = 20)  +
    scale_color_manual(values = c("darkgreen", "orange"))  + 
    scale_y_continuous(labels = scales::label_percent(), n.breaks = 8) +
    scale_linetype_manual(values = c(2,1, 3), labels = c("2.5% Quantile", "Average", "97.5% Quantile")) + 
    labs(x = "Age",
         y = str_wrap("Posterior probability for the number of postcodes with a detected inflation in expected prevalence under opportunistic screening to be lower than this at age 30",  width = 40)) + 
    scale_x_continuous(breaks = seq(30, 66, 5))

@@

plot_expected_prevalence <- results$prevalence$expected_prevalence %>% 
  plyr::rbind.fill(results$prevalence$expected_prevalence_year) %>% 
  mutate(year = ifelse(is.na(year), "All", year),
      year = factor(year, levels = c("2020","2021","2022","2023","All")),
      virus = ifelse(virus == "hpv1618", "HPV16/18", "Other genotypes"),
      test = paste0(test, " screening")) %>% 
  ggplot() + 
  geom_point(position = position_dodge(width = 0.9),
        aes(x = year, y = mean, color = test))+
  geom_errorbar(position = position_dodge(width = 0.9),
         aes(x = year, ymin = qi_lb, ymax = qi_ub, color = test))+
  #geom_hline(yintercept = 0, linetype = "dashed")+
  labs(x = "Year",
     y = "Expected prevalence in \n the analytic sample",
     caption = "Posterior average: dots, Posterior ETI95%: bars",
     color = "Assuming all tests collected through: ")+ 
  theme_minimal(base_size = 20) +
  facet_grid(~virus)+
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = scales::label_percent(), n.breaks = 8)+
  scale_color_manual(values = c("red", "blue"))

plot_ame <- results$ame$ame_test %>% 
  plyr::rbind.fill(results$ame$ame_test_year) %>% 
  mutate(year = ifelse(is.na(year), "All", year),
      year = factor(year, levels = c("2020","2021","2022","2023","All")),
      virus = ifelse(virus == "hpv1618", "HPV16/18", "Other genotypes")) %>% 
  ggplot() + 
  geom_point(aes(x = year, y = mean, color = year))+
  geom_errorbar(aes(x = year, ymin = qi_lb, ymax = qi_ub, color = year))+
  #geom_hline(yintercept = 0, linetype = "dashed")+
  labs(x = "Year",
     y = "Marginal difference in expected prevalence  of opportunistic screening",
     caption = "Posterior average: dots, Posterior ETI95%: bars",
     color = "Year: ")+ 
  theme_minimal(base_size = 20) +
  facet_grid(~virus)+
  theme(legend.direction = "horizontal", legend.position = "bottom")+
  scale_y_continuous(labels = function(x)100*x)

plot_ameage <- results$ame$ame_test_age %>% 
    plyr::rbind.fill(results$ame$ame_test %>% mutate(age_class = "[30,66]")) %>% 
    plyr::rbind.fill(results$ame$ame_test_year %>% mutate(age_class = "[30,66]")) %>% 
    plyr::rbind.fill(results$ame$ame_test_age_year) %>% 
    mutate(year = ifelse(is.na(year), "All", year),
           year = factor(year, levels = c("2020","2021","2022","2023","All")),
           virus = ifelse(virus == "hpv1618", "HPV16/18", "Other genotypes"),
           age_class = factor(age_class, levels = c("[30,39]", "(39,49]", "(49,59]", "(59,66]", "[30,66]"))) %>% 
    ggplot() + 
    geom_point(aes(x = year, y = mean, color = year))+
    geom_errorbar(aes(x = year, ymin = qi_lb, ymax = qi_ub, color = year))+
    facet_grid(age_class~virus) +
    #geom_hline(yintercept = 0, linetype = "dashed")+
    labs(x = "Year",
         y = "Marginal difference in expected prevalence  by age",
         caption = "Posterior average: dots, Posterior ETI95%: bars",
         color = "Year: ")+ 
    theme_minimal(base_size = 20) +
    theme(legend.direction = "horizontal", legend.position = "bottom")+
    scale_color_manual(values = c("darkorange", "purple", "darkgreen", "brown", "black"))+
    geom_hline(yintercept = 0, color = 'red', linetype = "dashed") + 
    scale_y_continuous(breaks = seq(0,0.06, 0.02), labels = function(x)paste0(100*x,"pp"))

plot_or_time <- results$list_main_city$summary_city_year %>% 
  filter(age == 30 &
        metric == "or" & 
        idtime != 1 & 
        city == "Paris") %>% 
  ggplot() +
  geom_point(aes(x = genotypes, y = mean, color = test ), position = position_dodge(width = 0.9))+
  geom_errorbar(aes(x = genotypes, ymin = qi_lb, ymax = qi_ub, color = test ), position = position_dodge(width = 0.9)) +
  theme_minimal()+
  geom_hline(yintercept = 1, linetype = "dashed") +
  scale_y_continuous(n.breaks = 8) +
  labs(x = "Genotypes",
     y = "Odds ratio of the expected \n prevalence  between the last \n and first week of the period",
     color = "Type of screening: ")+
  scale_color_manual(values = c("red", "blue")) +
   theme_minimal(base_size = 20) +
   theme(legend.direction = "horizontal", legend.position = "bottom") 
```

@@

p <- ggpubr::ggarrange(
ggpubr::ggarrange(
 space30_differencetest_hpv1618+
  labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none") +
  labs(subtitle = "Metropolitan France"),
 space30_differencetest_hpvother+ 
  labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none")+
  labs(subtitle = "Metropolitan France"),
 labels = c("A) ", "B) "),
 font.label = list(size = 20, color = "black", face = "bold", family = NULL)
 ),
ggpubr::ggarrange(
paris30_differencetest_hpv1618 +
  labs(subtitle = "Zoom on Paris region"),
paris30_differencetest_hpvother+
  labs(subtitle = "Zoom on Paris region"),
labels = c(" ", " "), 
nrow = 1),
heights = c(2,1),
nrow = 2)

@@

p <- ggpubr::ggarrange(
ggpubr::ggarrange(
france30_hpv1618 +
 labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none")+
  labs(subtitle = "Metropolitan France"),
france30_hpvother+
 labs(color = element_blank(), fill = element_blank())+
   theme(legend.position = "none")+
  labs(subtitle = "Metropolitan France"),
labels = c("A) ", "B) "),
 font.label = list(size = 20, color = "black", face = "bold", family = NULL)),
ggpubr::ggarrange(
paris30_hpv1618+
  labs(subtitle = "Zoom on Paris region"),
paris30_hpvother+
  labs(subtitle = "Zoom on Paris region"),
labels = c(" ", "")),
heights = c(2,1),
nrow = 2)

@@

```{r}
plot_cp <- ggpubr::ggarrange(
    plot_number_cp,
    diff_number_cp,
  labels = c("C) ", "D) "),
 font.label = list(size = 20, color = "black", face = "bold", family = NULL),
 ncol = 2)
```

@@

ggpubr::ggarrange(
  plot_summary_city,
  diff_between_test_city,
  plot_cp,
  labels = c("A) ", "B) ", " "),
 font.label = list(size = 20, color = "black", face = "bold", family = NULL),
  nrow = 3)

@@

`r text_sup`
